A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2020-10-14 05_calibration_data.Rmd
add griend remove segments

@@

```{r}
# patch with residence points and all patches
fig_basic_residence <-
  ggplot()+
  geom_sf(data = griend)+
  geom_point(data = data_res_summary, 
             aes(x_median, y_median),
             size = 10, shape = 7,
             # stroke = ,
             col = "grey20",
             alpha = 1)+
    # geom_path(data = data_recurse,
    #          aes(x, y),
    #         col = "grey", lwd = 0.2)+
  # geom_text(data = data_res_summary,
  #           aes(x_median, y_median,
  #               label = tID),
  #           # size = 10, shape = 7,
  #           # stroke = ,
  #           nudge_x = 100,
  #           fontface = "bold",
  #           col = "grey20",
  #           alpha = 1)+
  # geom_text(data = patch_summary_data, 
  #           aes(x_median, y_median,
  #               label = patch),
  #           # size = 10, shape = 7,
  #           # stroke = ,
  #           nudge_x = -50,
  #           fontface = "bold",
  #           col = pal[4],
  #           alpha = 1)+
  geom_point(data = data_recurse,
            aes(x, y,
                col = res_time > 5,
                shape = res_time > 5),
            show.legend = F,
            size = 2)+
  geom_sf(data = patch_sf_data,
          fill = pal[4],
          col = pal[4],
          alpha = 0.3)+
  geom_segment(data = patch_summary_data,
            aes(x = x_end, y = y_end,
                xend = shift(x_start, type = "lag"),
                yend = shift(y_start, type = "lag")),
            col = pal[4], lty = 1,
            lwd = 0.5)+
  # geom_point(data = patch_summary_data,
  #            aes(x_median, y_median),
  #            size = 5,
  #            stroke = 1,
  #            col = pal[4],
  #            shape = 1,
  #            show.legend = F)+
  scale_colour_manual(values = c("grey40", pal[3]))+
  scale_shape_manual(values = c(1, 19))+
  scale_fill_distiller(palette = "RdPu")+
  ggspatial::annotation_scale(location = "tl")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank(),
        panel.background = element_rect(fill = "grey99"))+
  coord_sf(crs = 32631,
           expand = F,
           ylim = c(5901700, 5903150),
           xlim = c(649300, 650700))
```

>>>>

### Read Griend

```{r}
# read griend
griend <- sf::st_read("data/griend_polygon/griend_polygon.shp")
```

@@

```{r}
# patch with residence points and all patches
fig_basic_residence <-
  ggplot()+
  geom_sf(data = griend)+
  geom_point(data = data_res_summary, 
             aes(x_median, y_median),
             size = 10, shape = 7,
             # stroke = ,
             col = "grey20",
             alpha = 1)+
    # geom_path(data = data_recurse,
    #          aes(x, y),
    #         col = "grey", lwd = 0.2)+
  # geom_text(data = data_res_summary,
  #           aes(x_median, y_median,
  #               label = tID),
  #           # size = 10, shape = 7,
  #           # stroke = ,
  #           nudge_x = 100,
  #           fontface = "bold",
  #           col = "grey20",
  #           alpha = 1)+
  # geom_text(data = patch_summary_data, 
  #           aes(x_median, y_median,
  #               label = patch),
  #           # size = 10, shape = 7,
  #           # stroke = ,
  #           nudge_x = -50,
  #           fontface = "bold",
  #           col = pal[4],
  #           alpha = 1)+
  geom_point(data = data_recurse,
            aes(x, y,
                col = res_time > 5,
                shape = res_time > 5),
            show.legend = F,
            size = 2)+
  geom_sf(data = patch_sf_data,
          fill = pal[4],
          col = pal[4],
          alpha = 0.3)+
  # geom_segment(data = patch_summary_data,
  #           aes(x = x_end, y = y_end,
  #               xend = shift(x_start, type = "lag"),
  #               yend = shift(y_start, type = "lag")),
  #           col = pal[4], lty = 1,
  #           lwd = 0.5)+
  # geom_point(data = patch_summary_data,
  #            aes(x_median, y_median),
  #            size = 5,
  #            stroke = 1,
  #            col = pal[4],
  #            shape = 1,
  #            show.legend = F)+
  scale_colour_manual(values = c("grey40", pal[3]))+
  scale_shape_manual(values = c(1, 19))+
  scale_fill_distiller(palette = "RdPu")+
  ggspatial::annotation_scale(location = "tl")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank(),
        panel.background = element_rect(fill = "grey99"))+
  coord_sf(crs = 32631,
           expand = F,
           ylim = c(5901700, 5903150),
           xlim = c(649300, 650700))
```
